Spatial Analysis of Russian Law Firms Naming

### 2024-07-18 law-firms-names/Paper.Rmd
Write paragraph about data, #5

>>>>

The issue of obtaining information about firm names is challenging. Even though all Russian organisations are registered in the unified state registry operated by Federal Tax Service (FTS of Russia), and an extract about a particular company from this registry can be downloaded online by any person free of charge, there is no straightforward way to get names of all companies from the registry at once without paying a considerable amount of money and without negotiating a contract with the responsible government body. There are a few commercial firms that re-cell the data from the registry of companies, but the prices are substantial. To overcome these problems, a Unified state registry of small and medium-sized businesses (SMB registry) was used. This registry has been maintained since 2016 according to the Article 4.1 of Federal Law of July 24, 2007 No 209-FZ “On the development of small and medium-sized businesses in the Russian Federation”. All the companies and individual entrepreneurs that have a yearly revenue below 2 billion roubles and an average yearly number of employees below 250 are automatically included in the SMB registry without any action required on their side. In contrast to the main registries of companies and entrepreneurs, SMB registry can be fully downloaded at the FTS open data portal free of charge, as well as the monthly history of its updates since the beginning of the operation. Thus, this registry can be treated as the most comprehensive free data source with the information about Russian business entities (organisations and individuals). The downloadable version of the registry includes, in particular, firm names, addresses of registration (up to a settlement), and codes of activity kinds according to the All-Russia Classifier of Kinds of Economic Activity. Large firms are not present in the registry, so some data is missing. However, the majority of commercial law firms in Russia (more than 75%) can be categorized as small and medium-sized businesses and are included in the registry, so the availability of information is relatively high, and it can be used for trustworthy conclusions.
